Throughout the past few terms, this project has been a large portion of the technical work that I have been a part of. One way that it has affected my technical experience is that it has opened my eyes to python which has for the moment become my go-to language. As the project is mostly written in Python, I have learned much about the language in general, and have also learned Flask. Inspired by the effectiveness of Flask in this project, I actually used Flask in a side project that I was doing by myself, which worked out quite well. This was my first real in-depth experience working with HTML and Javascript, and it taught me a lot about the difficulties and usefulness that working with them provides. I also learned a lot more about Git and how to use it effectively in a team environment. \\
This was also my first experience of working closely as a team with two other people for several months. The three of us worked well together and were able to assign tasks equally and without much effort. Working as a team was made much easier with source control tools like Git, and the use of an instant messaging service. We chose to use an IRC channel as our main chat room for discussing project-related activities, which was helpful in communication. Our frequent meetings allowed us to stay on task and up to date on what each of us were doing with the project. \\
If we were to do this project over again, there is not much that I would change. Our plan and course of action worked out well, and there were no grand mistakes with how we organized the project, although there were a couple points in the project where we ran a little bit close to the deadlines.